Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-24 ms.rmd
Rewording sentence to be more clear

The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small (). Considering acute responses of acclimated animals at high temperatures are also expected to increase (see above), acclimatization is not likely going to provide adaptive benefits under climate change.

>>>>

The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small (). Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
